---
title: "1-Normalisation&Clustering"
author: "Rebecca Ong"
date: "05/09/2024"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(STutility)
library(hdf5r)
library(ggplot2)
library(tidyr)
library(dplyr)
library(RColorBrewer)
library(SC3)
library(pander)
library(Palo)
```

# Set directory containing files
```{r}
setwd("~/file_path")
```

# Load data (spaceranger outputs)
Create a data.frame that contains all the paths to the required input files for all 12 samples (4 sham, 4 iTBS, 4 cTBS)
```{r}
sampleNames <- c('sham1', 'sham2', 'sham3', 'sham4', 'iTBS1', 'iTBS2', 'iTBS3', 'iTBS4', 'cTBS1', 'cTBS2', 'cTBS3', 'cTBS4')
infoTable <- data.frame(sampleNames)
rownames(infoTable) <- sampleNames
infoTable$samples <- c('sham1_filtered_feature_bc_matrix.h5', 'sham2_filtered_feature_bc_matrix.h5', 'sham3_filtered_feature_bc_matrix.h5', 'sham4_filtered_feature_bc_matrix.h5', 'iTBS1_filtered_feature_bc_matrix.h5', 'iTBS2_filtered_feature_bc_matrix.h5', 'iTBS3_filtered_feature_bc_matrix.h5', 'iTBS4_filtered_feature_bc_matrix.h5',
'cTBS1_filtered_feature_bc_matrix.h5',
'cTBS2_filtered_feature_bc_matrix.h5',
'cTBS3_filtered_feature_bc_matrix.h5',
'cTBS4_filtered_feature_bc_matrix.h5')
infoTable$spotfiles <- c('sham1_tissue_positions_list.csv', 'sham2_tissue_positions_list.csv', 'sham3_tissue_positions_list.csv', 'sham4_tissue_positions_list.csv', 'iTBS1_tissue_positions_list.csv', 'iTBS2_tissue_positions_list.csv', 'iTBS3_tissue_positions_list.csv', 'iTBS4_tissue_positions_list.csv',
'cTBS1_tissue_positions_list.csv',
'cTBS2_tissue_positions_list.csv',
'cTBS3_tissue_positions_list.csv',
'cTBS4_tissue_positions_list.csv')
infoTable$imgs <- c('sham1_tissue_hires_image.png', 'sham2_tissue_hires_image.png', 'sham3_tissue_hires_image.png', 'sham4_tissue_hires_image.png', 'iTBS1_tissue_hires_image.png', 'iTBS2_tissue_hires_image.png', 'iTBS3_tissue_hires_image.png', 'iTBS4_tissue_hires_image.png',
'cTBS1_tissue_hires_image.png',
'cTBS2_tissue_hires_image.png',
'cTBS3_tissue_hires_image.png',
'cTBS4_tissue_hires_image.png')
infoTable$json <- c('sham1_scalefactors_json.json', 'sham2_scalefactors_json.json', 'sham3_scalefactors_json.json', 'sham4_scalefactors_json.json', 'iTBS1_scalefactors_json.json', 'iTBS2_scalefactors_json.json', 'iTBS3_scalefactors_json.json', 'iTBS4_scalefactors_json.json',
'cTBS1_scalefactors_json.json',
'cTBS2_scalefactors_json.json',
'cTBS3_scalefactors_json.json',
'cTBS4_scalefactors_json.json')
```

## Create Seurat object
```{r}
seurat <- InputFromTable(infotable = infoTable,
                     minUMICountsPerGene = 100,
                     minGenesPerSpot = 5,
                     minSpotsPerGene = 500,
                     platform = "Visium")
```

## Load H&E images
```{r}
seurat <- LoadImages(seurat, time.resolve = FALSE, verbose= TRUE)
```


## Add sample and treatment identities into the Seurat object
```{r}
seurat$sample <- paste0("sample_", GetStaffli(seurat)[[,"sample", drop = T]])
for(i in 1:length(sampleNames)){
  temp = which(GetStaffli(seurat)[[,'sample']] ==i)
  seurat$sample[temp] = sampleNames[i]
}

treatment <- c('sham', 'sham', 'sham', 'sham', 'iTBS', 'iTBS', 'iTBS', 'iTBS', 'cTBS', 'cTBS', 'cTBS', 'cTBS')
seurat$treatment <- paste0("treatment_", GetStaffli(seurat)[[,"sample", drop = T]])
for(i in 1:length(treatment)){
  temp = which(GetStaffli(seurat)[[,"sample"]] ==i)
  seurat$treatment[temp] = treatment[i]
}
```

# Quality control
To look at the spatial distribution of number of genes detected per cell (nFeature_RNA)
```{r}
seurat@tools[["Staffli"]]@samplenames <- sampleNames
ST.FeaturePlot(object = seurat, features = "nFeature_RNA", indices = '12', ncol = 2, pt.size = 2.5)
FeatureOverlay(seurat, features ="nFeature_RNA")
```

To look at the spatial distribution of the number of UMIs detected per cell (nCount_RNA)
```{r}
ST.FeaturePlot(seurat, features = c("nCount_RNA"), indices = '12', ncol = 2, pt.size = 2.5)
```

## QC Plots
```{r}
# Number of unique genes per spot
ggplot() + geom_histogram(data = seurat[[]], aes(nFeature_RNA), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Unique genes per spot")

# Total counts per spots (combine all samples)
ggplot() + geom_histogram(data = seurat[[]], aes(nCount_RNA), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Total counts per spot")

gene_attr <- data.frame(nUMI = Matrix::rowSums(seurat@assays$RNA@counts),
                        nSpots = Matrix::rowSums(seurat@assays$RNA@counts > 0))

# Total counts per gene (log10 scale)
ggplot() + geom_histogram(data = gene_attr, aes(nUMI), fill = "red", alpha = 0.7, bins = 50) + scale_x_log10() + 
  ggtitle("Total counts per gene (log10scale)")

# Total spots per gene
ggplot () + geom_histogram(data = gene_attr, aes(nSpots), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Total spots per gene")
```

# Run analysis w/out sample 12 (cTBS4)
Plotting the UMI distribution on sample 12 (cTBS4), a large area appears to have no genes or UMIs detected i.e., blank. This is likely due to incomplete/unsuccessful permeabilisation of the tissue and thus no RNA was released and captured (permeabilisation enzyme was unevenly distirbuted in the well).

## Load data
```{r}
NocTBS4_sampleNames <- c('sham1', 'sham2', 'sham3', 'sham4', 'iTBS1', 'iTBS2', 'iTBS3', 'iTBS4', 'cTBS1', 'cTBS2', 'cTBS3')
NocTBS4_infoTable <- data.frame(NocTBS4_sampleNames)
rownames(NocTBS4_infoTable) <- NocTBS4_sampleNames
NocTBS4_infoTable$samples <- c('sham1_filtered_feature_bc_matrix.h5', 'sham2_filtered_feature_bc_matrix.h5', 'sham3_filtered_feature_bc_matrix.h5', 'sham4_filtered_feature_bc_matrix.h5', 'iTBS1_filtered_feature_bc_matrix.h5', 'iTBS2_filtered_feature_bc_matrix.h5', 'iTBS3_filtered_feature_bc_matrix.h5', 'iTBS4_filtered_feature_bc_matrix.h5',
'cTBS1_filtered_feature_bc_matrix.h5',
'cTBS2_filtered_feature_bc_matrix.h5',
'cTBS3_filtered_feature_bc_matrix.h5')
NocTBS4_infoTable$spotfiles <- c('sham1_tissue_positions_list.csv', 'sham2_tissue_positions_list.csv', 'sham3_tissue_positions_list.csv', 'sham4_tissue_positions_list.csv', 'iTBS1_tissue_positions_list.csv', 'iTBS2_tissue_positions_list.csv', 'iTBS3_tissue_positions_list.csv', 'iTBS4_tissue_positions_list.csv',
'cTBS1_tissue_positions_list.csv',
'cTBS2_tissue_positions_list.csv',
'cTBS3_tissue_positions_list.csv')
NocTBS4_infoTable$imgs <- c('sham1_tissue_hires_image.png', 'sham2_tissue_hires_image.png', 'sham3_tissue_hires_image.png', 'sham4_tissue_hires_image.png', 'iTBS1_tissue_hires_image.png', 'iTBS2_tissue_hires_image.png', 'iTBS3_tissue_hires_image.png', 'iTBS4_tissue_hires_image.png',
'cTBS1_tissue_hires_image.png',
'cTBS2_tissue_hires_image.png',
'cTBS3_tissue_hires_image.png')
NocTBS4_infoTable$json <- c('sham1_scalefactors_json.json', 'sham2_scalefactors_json.json', 'sham3_scalefactors_json.json', 'sham4_scalefactors_json.json', 'iTBS1_scalefactors_json.json', 'iTBS2_scalefactors_json.json', 'iTBS3_scalefactors_json.json', 'iTBS4_scalefactors_json.json',
'cTBS1_scalefactors_json.json',
'cTBS2_scalefactors_json.json',
'cTBS3_scalefactors_json.json')
```

## Create Seurat object
Create a Seurat object using the infoTable (with No cTBS4)
```{r}
NocTBS4_seurat <- InputFromTable(infotable = NocTBS4_infoTable,
                     minUMICountsPerGene = 100,
                     minGenesPerSpot = 5,
                     minSpotsPerGene = 500,
                     platform = "Visium")

# Load H&E images (no cTBS4)
NocTBS4_seurat <- LoadImages(NocTBS4_seurat, time.resolve = FALSE, verbose= TRUE)
ImagePlot(NocTBS4_seurat, method = "raster", type = "raw")

# Add sample identities into the Seurat object
NocTBS4_seurat$sample <- paste0("sample_", GetStaffli(NocTBS4_seurat)[[,"sample", drop = T]])
for(i in 1:length(NocTBS4_sampleNames)){
  temp = which(GetStaffli(NocTBS4_seurat)[[,'sample']] ==i)
  NocTBS4_seurat$sample[temp] = NocTBS4_sampleNames[i]
}

# Add treatment identities into the Seurat object
treatment <- c('sham', 'sham', 'sham', 'sham', 'iTBS', 'iTBS', 'iTBS', 'iTBS', 'cTBS', 'cTBS', 'cTBS')
NocTBS4_seurat$treatment <- paste0("treatment_", GetStaffli(NocTBS4_seurat)[[,"sample", drop = T]])
for(i in 1:length(treatment)){
  temp = which(GetStaffli(NocTBS4_seurat)[[,"sample"]] ==i)
  NocTBS4_seurat$treatment[temp] = treatment[i]
}
```

## Quality control
```{r}
# Number of unique genes per spot
ggplot() + geom_histogram(data = NocTBS4_seurat[[]], aes(nFeature_RNA), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Unique genes per spot")

# Total counts per spots (combine all samples)
ggplot() + geom_histogram(data = NocTBS4_seurat[[]], aes(nCount_RNA), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Total counts per spot")

NocTBS4_gene_attr <- data.frame(nUMI = Matrix::rowSums(NocTBS4_seurat@assays$RNA@counts),
                        nSpots = Matrix::rowSums(NocTBS4_seurat@assays$RNA@counts > 0))

# Total counts per gene (log10 scale)
ggplot() + geom_histogram(data = NocTBS4_gene_attr, aes(nUMI), fill = "red", alpha = 0.7, bins = 50) + scale_x_log10() + 
  ggtitle("Total counts per gene (log10scale)")

# Total spots per gene
ggplot () + geom_histogram(data = NocTBS4_gene_attr, aes(nSpots), fill = "red", alpha = 0.7, bins = 50) + ggtitle("Total spots per gene")
```

### Mitochondrial content
```{r}
mt.genes <- grep(pattern = "^mt-", x = rownames(NocTBS4_seurat), value = TRUE)
NocTBS4_seurat$percent.mito <- (Matrix::colSums(NocTBS4_seurat@assays$RNA@counts[mt.genes,])/Matrix::colSums(NocTBS4_seurat@assays$RNA@counts))*100
ST.FeaturePlot(NocTBS4_seurat, features = "percent.mito", pt.size = 1.5, ncol = 3)
```

### Ribosomal protein content
Identify the proportion of ribosomal protein coding genes per spot
```{r}
ribo.genes <- grep(pattern = "^Rp1|^Rps", x = rownames(NocTBS4_seurat), value = TRUE)
NocTBS4_seurat$percent.ribo <- (Matrix::colSums(NocTBS4_seurat@assays$RNA@counts[ribo.genes,])/Matrix::colSums(NocTBS4_seurat@assays$RNA@counts))*100
ST.FeaturePlot(NocTBS4_seurat, features = "percent.ribo", pt.size = 2.8, indices = 11)
```

## Filtering
```{r}
se.subset <- SubsetSTData(NocTBS4_seurat, expression = percent.mito < 30)
cat("Spots removed: ", ncol(NocTBS4_seurat) - ncol(se.subset), "\n")
ST.FeaturePlot(se.subset, features = "percent.mito", pt.size = 1.5, ncol = 3) + ggtitle("Keep spots with <30% mitochondrial content")
NocTBS4_subset <- se.subset
```

## Batch correction
```{r}
NocTBS4_subset_NoBatchCorrection <- NocTBS4_subset %>%
  SCTransform() %>%
  RunPCA() %>%
  RunUMAP(reduction = "pca", dims = 1:30)

NocTBS4_subset_BatchCorrected <- SCTransform(NocTBS4_subset, vars.to.regress = "sample")
NocTBS4_subset_BatchCorrected <- NocTBS4_subset_BatchCorrected %>%
  RunPCA() %>%
  RunUMAP(reduction = "pca", dims = 1:30)

p1 <- DimPlot(NocTBS4_subset_NoBatchCorrection, group.by = "sample", reduction = "umap") + ggtitle("No batch correction")
p2 <- DimPlot(NocTBS4_subset_BatchCorrected, group.by = "sample", reduction = "umap") + ggtitle("Batch corrected")
p1 - p2
```

## Flipping cTBS2 tissue sample
```{r}
flip_transform <- list("10" = list("mirror.x" = T))
NocTBS4_subset_BatchCorrected <- WarpImages(NocTBS4_subset_BatchCorrected, flip_transform)
```

# Clustering
```{r}
DimPlot(NocTBS4_subset_BatchCorrected, reduction = "pca")
DimHeatmap(NocTBS4_subset_BatchCorrected, dims = 1:10, cells = 500, balanced = TRUE)
ElbowPlot(NocTBS4_subset_BatchCorrected, ndims = 40)

NocTBS4_subset_BatchCorrected <- FindNeighbors(object = NocTBS4_subset_BatchCorrected, verbose = FALSE, reduction = "pca", dims = 1:30)
NocTBS4_subset_BatchCorrected <- FindClusters(object = NocTBS4_subset_BatchCorrected, verbose = FALSE, resolution = 0.2)
table(NocTBS4_subset_BatchCorrected$SCT_snn_res.0.1) # 7 clusters identified (resolution = 0.1)
table(NocTBS4_subset_BatchCorrected$SCT_snn_res.0.5) # 16 clusters identified (resolution = 0.5) but no L4 identified
table(NocTBS4_subset_BatchCorrected$SCT_snn_res.0.6) # 19 clusters identified (resolution = 0.6) but no L4 identified
table(NocTBS4_subset_BatchCorrected$SCT_snn_res.0.7) # 23 clusters identified (resolution = 0.7)

# Visualisation (at different clustering resolutions)
ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.1", pt.size = 2.8, ncol = 4, cols = col_vector), indices = 10)
p1 <- (ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.4", pt.size = 2.8, ncol = 4, cols = col_vector, indices = 10))
p2 <- (ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.6", pt.size = 2.8, ncol = 4, cols = col_vector, indices = 10)) 
p3 <- (ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.7", pt.size = 2.8, ncol = 4, cols = col_vector, indices = 10)) 
grid.arrange(p1, p2, p3, ncol = 3)

# Individual samples clustering
ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.5", pt.size = 3, cols = col_vector, indices = 11)

# Split clusters 
ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "SCT_snn_res.0.5", pt.size = 1.8, ncol = 4, split.labels = T, indices = 5, cols = col_vector)
```

## Relabelling clusters
```{r}
NocTBS4_subset_BatchCorrected$final_labels <- NocTBS4_subset_BatchCorrected$SCT_snn_res.0.5
levels(NocTBS4_subset_BatchCorrected$final_labels)
res0.5_annotated_labels <- c("Caudoputamen", "Ctx (layer 5)", "Ctx (layer 2/3)", "Ctx (other regions)", "Striatum ventral region", "Ctx (layer 6)", "Pallidum", "Ctx (layer 1)", "Corpus callosum", "Hypothalamus", "Lateral septal complex", "Unk1", "Lateral ventricle", "Unk2", "Unk3", "Unk4")
levels(NocTBS4_subset_BatchCorrected$final_labels) <- res0.5_annotated_labels

res0.5_annotated_labels_cols <- c("#B2DF8A", "#E7298A", "#FDBF6F", "#FFF2AE", "#BF5B17", "#386CB0", "#F4CAE4", "#666666", "#8DD3C7", "#BC80BD", "#7570B3", "#999999", "#A6CEE3","#B3B3B3", "#FFD92F", "#6A3D9A")

ST.FeaturePlot(object = NocTBS4_subset_BatchCorrected, features = "final_labels", pt.size = 3, ncol = 4, indices = 1, cols = res0.5_annotated_labels_cols)
```

