---
title: "2-DEGAnalysis"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(STutility)
library(hdf5r)
library(ggplot2)
library(tidyr)
library(dplyr)
library(RColorBrewer)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(generics)
library(clusterProfiler)
```

# Load seurat object
Load in .rds seurat object that has been batch corrected and contains all the clusters that will be used for identifying DEGs
```{r}
NocTBS4_subset_BatchCorrected <- readRDS(file.path("file_path", "NocTBS4_subset_BatchCorrected.rds"))
```

## Set Idents to compare between treatments
```{r}
Idents(NocTBS4_subset_BatchCorrected) <- NocTBS4_subset_BatchCorrected$treatment
```

# DEG analysis
## Cluster 1 -> CP (Caudoputamen)  (res 0.5)
```{r}
DEG_CP_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "1") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_CP_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "1") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_CP_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_CP_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_CP_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_CP_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_CP_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_CP_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CP_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_CP_iTBS <- DEG_CP_iTBS %>% drop_na()
DEG_CP_cTBS <- DEG_CP_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_CP_iTBS), rownames(DEG_CP_cTBS)))) #9
sum(table(rownames(DEG_CP_iTBS))) - sum(table(generics::intersect(rownames(DEG_CP_iTBS), rownames(DEG_CP_cTBS)))) #8
sum(table(rownames(DEG_CP_cTBS))) - sum(table(generics::intersect(rownames(DEG_CP_iTBS), rownames(DEG_CP_cTBS)))) #369
```

## Cluster 2 -> L5  (res 0.5)
```{r}
DEG_L5_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "2") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_L5_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "2") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_L5_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L5_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L5_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L5_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L5_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L5_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L5_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L5_iTBS <- DEG_L5_iTBS %>% drop_na()
DEG_L5_cTBS <- DEG_L5_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_L5_iTBS), rownames(DEG_L5_cTBS)))) #6
sum(table(rownames(DEG_L5_iTBS))) - sum(table(generics::intersect(rownames(DEG_L5_iTBS), rownames(DEG_L5_cTBS)))) #9
sum(table(rownames(DEG_L5_cTBS))) - sum(table(generics::intersect(rownames(DEG_L5_iTBS), rownames(DEG_L5_cTBS)))) #352
```

## Cluster 3 -> L2/3 (res 0.5)
```{r}
DEG_L2.3_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "3") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_L2.3_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "3") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_L2.3_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L2.3_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L2.3_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L2.3_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L2.3_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L2.3_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L2.3_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L2.3_iTBS <- DEG_L2.3_iTBS %>% drop_na()
DEG_L2.3_cTBS <- DEG_L2.3_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_L2.3_iTBS), rownames(DEG_L2.3_cTBS)))) #4
sum(table(rownames(DEG_L2.3_iTBS))) - sum(table(generics::intersect(rownames(DEG_L2.3_iTBS), rownames(DEG_L2.3_cTBS)))) #7
sum(table(rownames(DEG_L2.3_cTBS))) - sum(table(generics::intersect(rownames(DEG_L2.3_iTBS), rownames(DEG_L2.3_cTBS)))) #331
```

## Cluster 4 -> Ctx (other regions)
```{r}
DEG_Ctx.o_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "4") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_Ctx.o_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "4") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_Ctx.o_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_Ctx.o_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_Ctx.o_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_Ctx.o_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_Ctx.o_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_Ctx.o_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_Ctx.o_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_Ctx.o_iTBS <- DEG_Ctx.o_iTBS %>% drop_na()
DEG_Ctx.o_cTBS <- DEG_Ctx.o_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_Ctx.o_iTBS), rownames(DEG_Ctx.o_cTBS)))) #17
sum(table(rownames(DEG_Ctx.o_iTBS))) - sum(table(generics::intersect(rownames(DEG_Ctx.o_iTBS), rownames(DEG_Ctx.o_cTBS)))) #13
sum(table(rownames(DEG_Ctx.o_cTBS))) - sum(table(generics::intersect(rownames(DEG_Ctx.o_iTBS), rownames(DEG_Ctx.o_cTBS)))) #294
```

## Cluster 5 -> striatum ventral region (STRv)
```{r}
DEG_STRv_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "5") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_STRv_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "5") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_STRv_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_STRv_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_STRv_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_STRv_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_STRv_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_STRv_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_STRv_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_STRv_iTBS <- DEG_STRv_iTBS %>% drop_na()
DEG_STRv_cTBS <- DEG_STRv_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_STRv_iTBS), rownames(DEG_STRv_cTBS)))) #8
sum(table(rownames(DEG_STRv_iTBS))) - sum(table(generics::intersect(rownames(DEG_STRv_iTBS), rownames(DEG_STRv_cTBS)))) #7
sum(table(rownames(DEG_STRv_cTBS))) - sum(table(generics::intersect(rownames(DEG_STRv_iTBS), rownames(DEG_STRv_cTBS)))) #215
```

## Cluster 6 -> Ctx (layer 6)
```{r}
DEG_L6_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "6") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_L6_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "6") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_L6_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L6_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L6_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L6_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L6_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L6_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L6_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L6_iTBS <- DEG_L6_iTBS %>% drop_na()
DEG_L6_cTBS <- DEG_L6_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_L6_iTBS), rownames(DEG_L6_cTBS)))) #16
sum(table(rownames(DEG_L6_iTBS))) - sum(table(generics::intersect(rownames(DEG_L6_iTBS), rownames(DEG_L6_cTBS)))) #15
sum(table(rownames(DEG_L6_cTBS))) - sum(table(generics::intersect(rownames(DEG_L6_iTBS), rownames(DEG_L6_cTBS)))) #368
```

## Cluster 7 -> Pallidum (PAL)
```{r}
DEG_PAL_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "7") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_PAL_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "7") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_PAL_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_PAL_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_PAL_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_PAL_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_PAL_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_PAL_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_PAL_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_PAL_iTBS <- DEG_PAL_iTBS %>% drop_na()
DEG_PAL_cTBS <- DEG_PAL_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_PAL_iTBS), rownames(DEG_PAL_cTBS)))) #32
sum(table(rownames(DEG_PAL_iTBS))) - sum(table(generics::intersect(rownames(DEG_PAL_iTBS), rownames(DEG_PAL_cTBS)))) #20
sum(table(rownames(DEG_PAL_cTBS))) - sum(table(generics::intersect(rownames(DEG_PAL_iTBS), rownames(DEG_PAL_cTBS)))) #375
```

## Cluster 8 -> Ctx layer 1 (L1)
```{r}
DEG_L1_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "8") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_L1_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "8") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_L1_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L1_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L1_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L1_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_L1_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_L1_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_L1_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_L1_iTBS <- DEG_L1_iTBS %>% drop_na()
DEG_L1_cTBS <- DEG_L1_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_L1_iTBS), rownames(DEG_L1_cTBS)))) #16
sum(table(rownames(DEG_L1_iTBS))) - sum(table(generics::intersect(rownames(DEG_L1_iTBS), rownames(DEG_L1_cTBS)))) #13
sum(table(rownames(DEG_L1_cTBS))) - sum(table(generics::intersect(rownames(DEG_L1_iTBS), rownames(DEG_L1_cTBS)))) #368
```

## Cluster 9 -> corpus callosum (CC)
```{r}
DEG_CC_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "9") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_CC_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "9") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_CC_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_CC_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_CC_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_CC_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_CC_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_CC_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_CC_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_CC_iTBS <- DEG_CC_iTBS %>% drop_na()
DEG_CC_cTBS <- DEG_CC_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_CC_iTBS), rownames(DEG_CC_cTBS)))) #25
sum(table(rownames(DEG_CC_iTBS))) - sum(table(generics::intersect(rownames(DEG_CC_iTBS), rownames(DEG_CC_cTBS)))) #25
sum(table(rownames(DEG_CC_cTBS))) - sum(table(generics::intersect(rownames(DEG_CC_iTBS), rownames(DEG_CC_cTBS)))) #348
```

## Cluster 10 -> hypothalamus (HY)
```{r}
DEG_HY_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "10") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_HY_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "10") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_HY_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_HY_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_HY_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_HY_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_HY_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_HY_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_HY_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_HY_iTBS <- DEG_HY_iTBS %>% drop_na()
DEG_HY_cTBS <- DEG_HY_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_HY_iTBS), rownames(DEG_HY_cTBS)))) #38
sum(table(rownames(DEG_HY_iTBS))) - sum(table(generics::intersect(rownames(DEG_HY_iTBS), rownames(DEG_HY_cTBS)))) #13
sum(table(rownames(DEG_HY_cTBS))) - sum(table(generics::intersect(rownames(DEG_HY_iTBS), rownames(DEG_HY_cTBS)))) #439
```

## Cluster 11 -> lateral septal complex (LSX)
```{r}
DEG_LSX_iTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "11") %>% 
  FindMarkers(ident.1 = "iTBS", ident.2 = "sham")
DEG_LSX_cTBS <- SubsetSTData(NocTBS4_subset_BatchCorrected, expression = SCT_snn_res.0.5 == "11") %>% 
  FindMarkers(ident.1 = "cTBS", ident.2 = "sham")

# annotate
DEG_LSX_iTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_iTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_LSX_iTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_iTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_LSX_iTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_iTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_LSX_cTBS$symbol <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_cTBS), column="SYMBOL", keytype="SYMBOL", multiVals="first")
DEG_LSX_cTBS$genename <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_cTBS), column="GENENAME", keytype="SYMBOL", multiVals="first")
DEG_LSX_cTBS$entrezID <- mapIds(org.Mm.eg.db, keys=row.names(DEG_LSX_cTBS), column="ENTREZID", keytype="SYMBOL", multiVals="first")

DEG_LSX_iTBS <- DEG_LSX_iTBS %>% drop_na()
DEG_LSX_cTBS <- DEG_LSX_cTBS %>% drop_na()

# get number of overlapping DEGs between iTBS and cTBS
sum(table(generics::intersect(rownames(DEG_LSX_iTBS), rownames(DEG_LSX_cTBS)))) #17
sum(table(rownames(DEG_LSX_iTBS))) - sum(table(generics::intersect(rownames(DEG_LSX_iTBS), rownames(DEG_LSX_cTBS)))) #16
sum(table(rownames(DEG_LSX_cTBS))) - sum(table(generics::intersect(rownames(DEG_LSX_iTBS), rownames(DEG_LSX_cTBS)))) #420
```

# Significant DEGs (p.adj<0.05, abs(avg_log2FC) > 0.25)
```{r}
# subcortical
DEG_CP_iTBS_Sig <- subset(DEG_CP_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_CP_cTBS_Sig <- subset(DEG_CP_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_CC_iTBS_Sig <- subset(DEG_CC_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_CC_cTBS_Sig <- subset(DEG_CC_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_HY_iTBS_Sig <- subset(DEG_HY_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_HY_cTBS_Sig <- subset(DEG_HY_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_LSX_iTBS_Sig <- subset(DEG_LSX_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_LSX_cTBS_Sig <- subset(DEG_LSX_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_PAL_iTBS_Sig <- subset(DEG_PAL_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_PAL_cTBS_Sig <- subset(DEG_PAL_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_STRv_iTBS_Sig <- subset(DEG_STRv_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_STRv_cTBS_Sig <- subset(DEG_STRV_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

# cortical
DEG_L1_iTBS_Sig <- subset(DEG_L1_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_L1_cTBS_Sig <- subset(DEG_L1_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_L2.3_iTBS_Sig <- subset(DEG_L2.3_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_L2.3_cTBS_Sig <- subset(DEG_L2.3_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_L5_iTBS_Sig <- subset(DEG_L5_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_L5_cTBS_Sig <- subset(DEG_L5_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_L6_iTBS_Sig <- subset(DEG_L6_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_L6_cTBS_Sig <- subset(DEG_L6_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)

DEG_Ctx.o_iTBS_Sig <- subset(DEG_Ctx.o_iTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
DEG_Ctx.o_cTBS_Sig <- subset(DEG_Ctx.o_cTBS, p_val_adj <= 0.05 & abs(avg_log2FC) > 0.25)
```

# GO analysis
```{r}
## Cluster 1 -> caudoputamen
DEG_CP_iTBS_Sig <- DEG_CP_iTBS_Sig[order(DEG_CP_iTBS_Sig$p_val_adj),]
iTBS.CP_genelist <- DEG_CP_iTBS_Sig[,8]
sum(table(iTBS.CP_genelist)) #17
iTBS.CP_GO <- enrichGO(iTBS.CP_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_CP_cTBS_Sig <- DEG_CP_cTBS_Sig[order(DEG_CP_cTBS_Sig$p_val_adj),]
cTBS.CP_genelist <- DEG_CP_cTBS_Sig[,8]
sum(table(cTBS.CP_genelist)) #378
cTBS.CP_GO <- enrichGO(cTBS.CP_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 2 -> layer 5
DEG_L5_iTBS_Sig <- DEG_L5_iTBS_Sig[order(DEG_L5_iTBS_Sig$p_val_adj),]
iTBS.L5_genelist <- DEG_L5_iTBS_Sig[,8]
sum(table(iTBS.L5_genelist)) #15
iTBS.L5_GO <- enrichGO(iTBS.L5_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_L5_cTBS_Sig <- DEG_L5_cTBS_Sig[order(DEG_L5_cTBS_Sig$p_val_adj),]
cTBS.L5_genelist <- DEG_L5_cTBS_Sig[,8]
sum(table(cTBS.L5_genelist)) ##358
cTBS.L5_GO <- enrichGO(cTBS.L5_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 3 -> layer 2/3
DEG_L2.3_iTBS_Sig <- DEG_L2.3_iTBS_Sig[order(DEG_L2.3_iTBS_Sig$p_val_adj),]
iTBS.L2.3_genelist <- DEG_L2.3_iTBS_Sig[,8]
sum(table(iTBS.L2.3_genelist)) #11
iTBS.L2.3_GO <- enrichGO(iTBS.L2.3_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_L2.3_cTBS_Sig <- DEG_L2.3_cTBS_Sig[order(DEG_L2.3_cTBS_Sig$p_val_adj),]
cTBS.L2.3_genelist <- DEG_L2.3_cTBS_Sig[,8]
sum(table(cTBS.L2.3_genelist)) #333
cTBS.L2.3_GO <- enrichGO(cTBS.L2.3_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 4 -> Ctx (other regions)
DEG_Ctx.o_iTBS_Sig <- DEG_Ctx.o_iTBS_Sig[order(DEG_Ctx.o_iTBS_Sig$p_val_adj),]
iTBS.Ctx.o_genelist <- DEG_Ctx.o_iTBS_Sig[,8]
sum(table(iTBS.Ctx.o_genelist)) #29
iTBS.Ctx.o_GO <- enrichGO(iTBS.Ctx.o_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_Ctx.o_cTBS_Sig <- DEG_Ctx.o_cTBS_Sig[order(DEG_Ctx.o_cTBS_Sig$p_val_adj),]
cTBS.Ctx.o_genelist <- DEG_Ctx.o_cTBS_Sig[,8]
sum(table(cTBS.Ctx.o_genelist)) #306
cTBS.Ctx.o_GO <- enrichGO(cTBS.Ctx.o_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 5 -> striatum ventral region (STRv)
DEG_STRv_iTBS_Sig <- DEG_STRv_iTBS_Sig[order(DEG_STRv_iTBS_Sig$p_val_adj),]
iTBS.STRv_genelist <- DEG_STRv_iTBS_Sig[,8]
sum(table(iTBS.STRv_genelist)) #12
iTBS.STRv_GO <- enrichGO(iTBS.STRv_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_STRv_cTBS_Sig <- DEG_STRv_cTBS_Sig[order(DEG_STRv_cTBS_Sig$p_val_adj),]
cTBS.STRv_genelist <- DEG_STRv_cTBS_Sig[,8]
sum(table(cTBS.STRv_genelist)) #220
cTBS.STRv_GO <- enrichGO(cTBS.STRv_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 6 -> layer 6
DEG_L6_iTBS_Sig <- DEG_L6_iTBS_Sig[order(DEG_L6_iTBS_Sig$p_val_adj),]
iTBS.L6_genelist <- DEG_L6_iTBS_Sig[,8]
sum(table(iTBS.L6_genelist)) #29
iTBS.L6_GO <- enrichGO(iTBS.L6_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_L6_cTBS_Sig <- DEG_L6_cTBS_Sig[order(DEG_L6_cTBS_Sig$p_val_adj),]
cTBS.L6_genelist <- DEG_L6_cTBS_Sig[,8]
sum(table(cTBS.L6_genelist)) #370
cTBS.L6_GO <- enrichGO(cTBS.L6_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 7 -> Pallidum (PAL)
DEG_PAL_iTBS_Sig <- DEG_PAL_iTBS_Sig[order(DEG_PAL_iTBS_Sig$p_val_adj),]
iTBS.PAL_genelist <- DEG_PAL_iTBS_Sig[,8]
sum(table(iTBS.PAL_genelist)) #50
iTBS.PAL_GO <- enrichGO(iTBS.PAL_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_PAL_cTBS_Sig <- DEG_PAL_cTBS_Sig[order(DEG_PAL_cTBS_Sig$p_val_adj),]
cTBS.PAL_genelist <- DEG_PAL_cTBS_Sig[,8]
sum(table(cTBS.PAL_genelist)) #400
cTBS.PAL_GO <- enrichGO(cTBS.PAL_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 8 -> layer 1
DEG_L1_iTBS_Sig <- DEG_L1_iTBS_Sig[order(DEG_L1_iTBS_Sig$p_val_adj),]
iTBS.L1_genelist <- DEG_L1_iTBS_Sig[,8]
sum(table(iTBS.L1_genelist)) #23
iTBS.L1_GO <- enrichGO(iTBS.L1_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_L1_cTBS_Sig <- DEG_L1_cTBS_Sig[order(DEG_L1_cTBS_Sig$p_val_adj),]
cTBS.L1_genelist <- DEG_L1_cTBS_Sig[,8]
sum(table(cTBS.L1_genelist)) #345
cTBS.L1_GO <- enrichGO(cTBS.L1_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 9 -> corpus callosum (CC)
DEG_CC_iTBS_Sig <- DEG_CC_iTBS_Sig[order(DEG_CC_iTBS_Sig$p_val_adj),]
iTBS.CC_genelist <- DEG_CC_iTBS_Sig[,8]
sum(table(iTBS.CC_genelist)) #45
iTBS.CC_GO <- enrichGO(iTBS.CC_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_CC_cTBS_Sig <- DEG_CC_cTBS_Sig[order(DEG_CC_cTBS_Sig$p_val_adj),]
cTBS.CC_genelist <- DEG_CC_cTBS_Sig[,8]
sum(table(cTBS.CC_genelist)) #272
iTBS.CC_GO <- enrichGO(iTBS.CC_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 10 <- hypothalamus (HY)
DEG_HY_iTBS_Sig <- DEG_HY_iTBS_Sig[order(DEG_HY_iTBS_Sig$p_val_adj),]
iTBS.HY_genelist <- DEG_HY_iTBS_Sig[,8]
sum(table(iTBS.HY_genelist)) #41
iTBS.HY_GO <- enrichGO(iTBS.HY_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_HY_cTBS_Sig <- DEG_HY_cTBS_Sig[order(DEG_HY_cTBS_Sig$p_val_adj),]
cTBS.HY_genelist <- DEG_HY_cTBS_Sig[,8]
sum(table(cTBS.HY_genelist)) #412
cTBS.HY_GO <- enrichGO(cTBS.HY_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

## Cluster 11 -> lateral septal complex (LSX)
DEG_LSX_iTBS_Sig <- DEG_LSX_iTBS_Sig[order(DEG_LSX_iTBS_Sig$p_val_adj),]
iTBS.LSX_genelist <- DEG_LSX_iTBS_Sig[,8]
sum(table(iTBS.LSX_genelist)) #26
iTBS.LSX_GO <- enrichGO(iTBS.LSX_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)

DEG_LSX_cTBS_Sig <- DEG_LSX_cTBS_Sig[order(DEG_LSX_cTBS_Sig$p_val_adj),]
cTBS.LSX_genelist <- DEG_LSX_cTBS_Sig[,8]
sum(table(cTBS.LSX_genelist)) #398
cTBS.LSX_GO <- enrichGO(cTBS.LSX_genelist, OrgDb = org.Mm.eg.db, keyType = "ENTREZID", ont = "ALL", pAdjustMethod = "BH", pvalueCutoff = 0.01, qvalueCutoff = 0.05, readable = TRUE)
```
